These might seem harsh. 
They are worded firmly not because we're angry about it but because we mean business and violations are unacceptable.
\section{Characters}
\subsection{Age}
No characters under 18 years old.
No Played Bys under 18.
No players under 18.
We don't need the headaches.
\subsection{Concepts}
We hope that there is plenty of room in our game for a wide variety of characters.
Players are nothing if not creative, and you'll come up with things we never thought of or anticipated.
This is wonderful.
Stuff that is really strange will require extra thought on our part.
To help everyone out, in addition to a 'Background' writeup, we may also request (or you could pre-emptively supply,) a {\em Rationale} for their character.
The idea is to describe where you see the character going, why you are making decisions and other OOC information you'd like Staff to consider.
Please take advantage of this.
\subsection{Applications}
Everyone has standards.
All applications must meet certain requirements, tho individual spheres may have their own.
\section{Items}
\subsection{Super-Tech}
If you can't buy it somewhere, you can't make it using mundane techniques.
SUPER-tech is SUPER-natural in nature.
I don't care it it's an a movie.

\subsection{Crafting}
Crafting is one of those Special Snowflake sorts of deals. You are, and if
you buy the skills, you should get to use them. But the harder you make
your request on staff, the farther down the queue it slips. Some stuff,
we'll just say `no' because it's too complex to make/require
years of research to get the techniques.
\subsection{Ubiquity}
Any item that becomes commonplace will probably get nerfed. That implies
it grants an advantage that can't  be lived without, and so it's
overpowered.
