These are the OOC principals that guide our philosophy
\section{Fairness}
{\em People will be treated fairly; They will not be treated identically.}

This is one of the two definitions of `fair' you'll find in a
dictionary. Not everyone is the same. Some people will show that they
can be trusted with more responsibility than others. Some people will be
given more lattitude in their actions that others. Some folks need less
oversight, some need more. It is unfair to restrict everyone because of
the misbehavior of a few. It is unfair to give potentially disruptive
things into hands of people who have shown a disregard for others. Show
us you can be trusted to make things fun for everyone and you'll be
given more leeway.
\section{Rules}
{\em The rules are shared, if you abuse them, they will be taken away from you personally.}

Abuse item creation, certain merits, supernatural abilities and you'll
find us denying your ability to use them. You'll get a warning, probably
several, unless the abuse is unquestionably egregious or malicious. It
would be unfair to punish others for the abuses of a few.
\section{Snowflakes}
{\em You are special, just like everyone else.}

There is no creature exactly like you anywhere in time or space. You
can prove this mathematically. But so is everyone else. If you ask for
things that are unique, it will take longer. If you ask for unusual
or questionable things, the answer might be `no'. It might also be
`no, but...'
\section{Respect}
{\em We are all here for the fun; If it's fun for you but not for others, please refrain.}

This means things that `leak' beyond the immediate participants. Things
like rape, child abuse and random PKs are `leaky' in that people who
hear about these things feel compelled to become involved. We’re not
saying these don’t generate interesting play for some groups, we are
saying that they almost always end up ruining the fun for other people
than the immediately involved groups.
\section{Winning}
{\em This is not a zero-sum game.}

This is a cooperative game. Everyone who plays should be a winner
OOCly. The failure condition is having a bad time. This OOC idea extends
into IC space in so far as there is the kind of griefing that people
seem to love. Don;t do it.  If you have to win -- and in order for you
to win others must lose -- you need to find someplace else to play. We
suggest online poker.
\section{Focus}
{\em This isn't D\&D.}

Evrything should not revolve around combat or a dice roll. The size
of your dice-pool should not measure your value as a character. Combat
focussed characters will be de-incentivized. Upgrading your gear is not
part of character advancement.
