\section{Introduction}
Santa Carla is a conglomeration of features found in towns on the central/northern California coast from Santa Barbara to Eureka. It is geographically located on Monterey Bay, roughly in the location of the town of Moss Landing, between Santa Cruz and Monterey. We are playing with the geography and history of the area significantly.
\section{Recent History}
There was a war. One of those nasty ones fought in the shadows away from sight. The kind where they never find the bodies, only the charred husks of burnt-out homes and missing-persons reports. Sure, the whole thing was about meth traffic, right?

The town is isolated, with a thirty minute drive to the nearby cities. There is a large population of transients: Students, the homeless, migrant labor. The central coast has had more than its share of serial killers and ritual murder. Bad stuff has happened here, and people ignored it. Ignored it until it festered, and got bad enough that it had to be Taken Care Of. And it was. The larger organizations from `Over The Hill' banded up and stepped on them hard.
\section{State of things}

\begin{itemize}
\item The various PC supers know about and communicate with each-other. Some Lost saw you tossing magic around? No need to kill the guy to protect some secret, they know about the Mages and vice versa.
\item There are no general PC adversaries. All adversary characters are NPC or staff props. That guy you're talking to might be a Hunter, but if he is, it's for plot purposes and not a independent PC.
\item There are PC `werewolves' but they are part of Changing Breeds, not the Pure/Forsaken, and use the CB rules and culture.
\item There is a community of Lost and several Freeholds have been established.
\item There is a group of Mages that operate under the aegis of the South Bay Assembly. Yes, the Free Council holds sway here.
\item The war left its share of restless dead, so the Sin Eaters have moved in in the wake.
\item There are a few Families with roots in the area. They have no particular ties to or history with the supernatural.
\end{itemize}
\section{Thematic choices}
These are the principals which guide us in shaping the IC world.
\subsection{The focus of action is on earth.}
The Hedge, the Underworld, the Spirit Lands, the Twilight: These things exist but are not the place where your problems start. They are also dangerous. Extremely so. 
